Frequent Payment \thanks{}

### 2019-08-30 Tables/te.tex
worked on take up, and on the TE dofile

      & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} \\

@@

\multicolumn{1}{l}{No choice/Fee} & \multicolumn{1}{l}{0.11***} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-5.88*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.076***} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.068*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.11***} & \multicolumn{1}{l}{} \\
\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.023)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(3.20)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.026)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.038)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{} \\
\multicolumn{1}{l}{No choice/No fee} & \multicolumn{1}{l}{-0.0048} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-0.30} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-0.011} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.092*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.053***} & \multicolumn{1}{l}{} \\
\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(3.71)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.024)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.051)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.014)} & \multicolumn{1}{l}{} \\
      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.14***} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -6.81*} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.097**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.41***} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.29***} \\
\multicolumn{1}{l}{Choice/Fee} & \multicolumn{1}{l}{-0.0020} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.037)} & \multicolumn{1}{l}{1.58} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (3.82)} & \multicolumn{1}{l}{0.0044} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.042)} & \multicolumn{1}{l}{0.10**} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.096)} & \multicolumn{1}{l}{0.029**} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.034)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.021)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.018} & \multicolumn{1}{l}{(3.32)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 2.89} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.0060} & \multicolumn{1}{l}{(0.039)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 0.065*} & \multicolumn{1}{l}{(0.013)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.000012} \\
      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.021)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (3.49)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.022)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.039)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.012)} \\
\cmidrule{9-9}\cmidrule{11-11}      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -0.037} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -8.66**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -0.058**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.073} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.082***} \\
\multicolumn{1}{l}{Choice/No fee} & \multicolumn{1}{l}{-0.0066} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.026)} & \multicolumn{1}{l}{-3.31} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (4.09)} & \multicolumn{1}{l}{-0.018} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.029)} & \multicolumn{1}{l}{-0.0012} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.057)} & \multicolumn{1}{l}{0.019} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.018)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 0.0070} & \multicolumn{1}{l}{(3.43)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -1.13} & \multicolumn{1}{l}{(0.023)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.00055} & \multicolumn{1}{l}{(0.037)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.035} & \multicolumn{1}{l}{(0.011)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.010} \\
      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.025)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (3.88)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.026)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.038)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.012)} \\

@@

\multicolumn{1}{l}{Constant (Control)} & \multicolumn{1}{l}{0.44***} & \multicolumn{1}{l}{0.44***} & \multicolumn{1}{l}{92.4***} & \multicolumn{1}{l}{92.4***} & \multicolumn{1}{l}{-0.35***} & \multicolumn{1}{l}{-0.35***} & \multicolumn{1}{l}{0.99***} & \multicolumn{1}{l}{0.99***} & \multicolumn{1}{l}{0.12***} & \multicolumn{1}{l}{0.12***} \\
\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{(2.53)} & \multicolumn{1}{l}{(2.53)} & \multicolumn{1}{l}{(0.017)} & \multicolumn{1}{l}{(0.017)} & \multicolumn{1}{l}{(0.028)} & \multicolumn{1}{l}{(0.028)} & \multicolumn{1}{l}{(0.0085)} & \multicolumn{1}{l}{(0.0085)} \\

@@

\multicolumn{1}{l}{Observations} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{6119} & \multicolumn{1}{l}{6119} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} \\
\multicolumn{1}{l}{R-sq} & \multicolumn{1}{l}{0.007} & \multicolumn{1}{l}{0.010} & \multicolumn{1}{l}{0.003} & \multicolumn{1}{l}{0.005} & \multicolumn{1}{l}{0.003} & \multicolumn{1}{l}{0.005} & \multicolumn{1}{l}{0.002} & \multicolumn{1}{l}{0.006} & \multicolumn{1}{l}{0.010} & \multicolumn{1}{l}{0.028} \\
\multicolumn{1}{l}{Dependent Var Mean} & \multicolumn{2}{c}{0.46} & \multicolumn{2}{c}{90.8} & \multicolumn{2}{c}{-0.34} & \multicolumn{2}{c}{1.04} & \multicolumn{2}{c}{0.16} \\

>>>>

      & \multicolumn{2}{c}{Un-pledge} & \multicolumn{2}{c}{Days to un-pledge} & \multicolumn{2}{c}{Number of payments} & \multicolumn{2}{c}{Percentage of payment} & \multicolumn{2}{c}{Refrendum} \\

@@

\multicolumn{1}{l}{No choice/Fee} & \multicolumn{1}{c}{0.11***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-8.61***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.74***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.076***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.058**} & \multicolumn{1}{c}{} \\
      & \multicolumn{1}{c}{(0.023)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(2.83)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.19)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.026)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.022)} & \multicolumn{1}{c}{} \\
\multicolumn{1}{l}{No choice/Promise} & \multicolumn{1}{c}{-0.0014} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.23} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.62***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.0072} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{} \\
\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(3.31)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.21)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.025)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.024)} & \multicolumn{1}{c}{} \\
      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0093} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 1.91} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.28} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0093} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.0094} \\
\multicolumn{1}{l}{Choice/Fee} & \multicolumn{1}{c}{0.0064} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.020)} & \multicolumn{1}{c}{0.97} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (3.24)} & \multicolumn{1}{c}{0.71***} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.21)} & \multicolumn{1}{c}{-0.0025} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.021)} & \multicolumn{1}{c}{0.019} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.022)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.020)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.14***} & \multicolumn{1}{c}{(3.06)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -5.44} & \multicolumn{1}{c}{(0.26)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 4.49***} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.054} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.11***} \\
      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.038)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (4.29)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (1.21)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.042)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.036)} \\
      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.014} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -1.18} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.11} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0013} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.030} \\
\multicolumn{1}{l}{Choice/Promise} & \multicolumn{1}{c}{-0.0027} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.024)} & \multicolumn{1}{c}{-2.87} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (3.83)} & \multicolumn{1}{c}{0.26} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.22)} & \multicolumn{1}{c}{-0.015} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.026)} & \multicolumn{1}{c}{-0.012} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.027)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -0.040} & \multicolumn{1}{c}{(3.35)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -6.93*} & \multicolumn{1}{c}{(0.19)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 1.05***} & \multicolumn{1}{c}{(0.024)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -0.045} & \multicolumn{1}{c}{(0.023)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.028} \\
      & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.025)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (3.75)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.30)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.034)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.025)} \\

@@

\multicolumn{1}{l}{Constant} & \multicolumn{1}{c}{0.47***} & \multicolumn{1}{c}{0.46***} & \multicolumn{1}{c}{82.5***} & \multicolumn{1}{c}{83.5***} & \multicolumn{1}{c}{1.68***} & \multicolumn{1}{c}{1.32***} & \multicolumn{1}{c}{0.70***} & \multicolumn{1}{c}{0.69***} & \multicolumn{1}{c}{0.26***} & \multicolumn{1}{c}{0.24***} \\
\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.029)} & \multicolumn{1}{c}{(0.028)} & \multicolumn{1}{c}{(3.81)} & \multicolumn{1}{c}{(3.82)} & \multicolumn{1}{c}{(0.30)} & \multicolumn{1}{c}{(0.32)} & \multicolumn{1}{c}{(0.031)} & \multicolumn{1}{c}{(0.031)} & \multicolumn{1}{c}{(0.027)} & \multicolumn{1}{c}{(0.027)} \\

@@

\multicolumn{1}{l}{Observations} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{6118} & \multicolumn{1}{c}{6118} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} \\
\multicolumn{1}{l}{R-squared} & \multicolumn{1}{c}{0.013} & \multicolumn{1}{c}{0.016} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.025} & \multicolumn{1}{c}{0.005} & \multicolumn{1}{c}{0.014} & \multicolumn{1}{c}{0.009} & \multicolumn{1}{c}{0.010} & \multicolumn{1}{c}{0.028} & \multicolumn{1}{c}{0.029} \\
\multicolumn{1}{l}{Dependent Var Mean} & \multicolumn{1}{c}{0.46} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{91.0} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{2.57} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.75} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.36} & \multicolumn{1}{c}{} \\
\multicolumn{1}{l}{Branch FE} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} \\
\multicolumn{1}{l}{Dow FE} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} \\
